Behavior Driven Development in Haskell

### 2012-05-25 paper.tex
behaviors -> behavior

We agree that type signatures are good abstract document~\cite{free}
but there are many
functions whose behaviors cannot be guessed from their names and type
signatures. A good example is \verb|nub :: [a] -> [a]| in 
the Data.List module.

>>>>

We agree that type signatures are good abstract document~\cite{free}
but there are many
functions whose behavior cannot be guessed from their names and type
signatures. A good example is \verb|nub :: [a] -> [a]| in 
the Data.List module.
